% LaTeX resume using res.cls
\documentclass[margin,line,letterpaper]{res}
\topmargin=-.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=1in
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{mathpazo} % add possibly `sc` and `osf` options
\usepackage{eulervm}
\begin{document}

\name{HAO WU}
% \address used twice to have two lines of address
% IN CHINA
% \address{\small $\bullet$ wu.hao.cz.21@gmail.com $\bullet$ +86 158-9508-0059 $\bullet$ 800 Dongchuan Rd. Shanghai China, 200240}
% IN PA
\address{ $\bullet$ linkedin.com/in/hao-wu-710254128 $\bullet$ wu.hao.cz.21@gmail.com $\bullet$ (412)-616-6280}
%$\bullet$ Apt.603, South Aiken Ave., Pittsburgh, PA, 15232
\vspace{-.1 in}
\begin{resume}

\section{EDUCATION}
{
\small
\textbf{Carnegie Mellon University}\hfill Pittsburgh, PA (Expected) \\ Information Networking Institute\hfill Aug. 2017 --- May. 2019\\
Master of Science in Information Networking\\
{\small Selected Coursework: Introduction to Computer Systems (15-513, 2017Fall), Packet Switching and Computer Networks(18-756, 2017Fall)} 
}
\vspace{-.1 in}

{
\small
\textbf{Shanghai Jiao Tong University}\hfill Shanghai, China \\
University of Michigan - Shanghai Jiao Tong University Joint Institute (UM-SJTU JI) \hfill Sept. 2013 --- Aug. 2017\\
Bachelor of Engineering, Electrical and Computer Engineering
}
\vspace{-.05 in}
\section{SKILLS}
{\small \textbf{Programming/ScriptingLanguages:} (Proficient) C, C++, Python; (Familiar) SQL, MATLAB, Verilog}\\
{\small \textbf{Platforms:} Linux, Unix-like Systems, Windows, Mac OSX}\\
{\small \textbf{Frameworksand tools:} Django, Docker, Spark, Keras, Git, \LaTeX}
\vspace{-.05 in}
\section{EXPERIENCE}
{\small
{\bf\normalsize Intel Asia-Pacific R\&D Ltd.} \hfill Shanghai, China \\
{\it Big Data Team, Software Engineering Intern} \hfill Aug. 2016 --- Dec. 2016
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Participated in construction of a Docker based infrastructure management \& DevOps automation for big data systems and designed plugins to developed node management platform for ETCD system}
\item {\small Improved user interface to better list applications that are under management}
\end{itemize}
\vspace{-.1 in}
{\small
{\bf\normalsize Data \& Knowledge Management Lab}   \hfill Shanghai, China\\
{\it Shanghai Jiao Tong University, Research Student} \hfill Apr. 2016 --- Aug. 2016
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Applied K-means algorithm to realize user and job clustering, then built recommendation system with given user features to predict job postings that a user would prefer to click on}
\end{itemize}
\vspace{-.1 in}
{
\small
{\bf\normalsize Teaching Assistant} \hfill Shanghai, China\\
{Introduction to Cryptography, UM-SJTU JI} \hfill Apr. 2017 --- Aug. 2017\\
{Introduction to Operating System, UM-SJTU JI} \hfill Sept. 2016 --- Dec. 2016\\
{Introduction to Logic Design, UM-SJTU JI} \hfill May. 2016 --- Aug. 2016 \\
{Introduction to Computer and Programming, UM-SJTU JI}\hfill Sept. 2015 --- Dec. 2015
}
\vspace{-.05 in}

\section{SELECTED\\PROJECTS}
{
\small
{\bf Online Judge System for Cryptography Course} \hfill Apr. 2017 --- Aug. 2017\\
{\it Introduction to Cryptography, UM-SJTU JI}
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Developed online judge website by Django for students to realize black-box attack upon the cryptographic protocols implemented by others and to inquire current scoreboard}
\end{itemize}
\vspace{-.1 in}

{
\small
{\bf Machine Learning: Think and Speak} \hfill Apr. 2016 --- Dec. 2016\\
{\it \textbf{Team Leader}, Capstone with {\bf Siemens}}
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Developed intelligent sensor monitoring system based on Python for the manufacturing scenario which could collect sensor data to database}
\item {\small Applied neural networks (Keras) based on collected data to recognize type of component and detect exceptional situations, then reported predictions at interactive mobile client which is controlled by voice input}
\end{itemize}
\vspace{-.1 in}
{
\small
{\bf Shallow Discourse Parsing of Implicit Discourse Relations} \hfill Apr. 2016 ---  Aug. 2016\\
{\it Shanghai Jiao Tong University}
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Applied Maximum Entropy Model by Python and achieved 40.5\% accuracy, same as the world best result in 2009}
\item {\small Introduced word embedding into CNN (Keras) model and improved accuracy to 46.79\%}
\end{itemize}
\vspace{-.1 in}
%------------------------------------------
%{
%\small
%{\bf Personalized Job Recommendation in XING.com } \hfill Apr. 2016 --- Aug. 2016\\
%{\it \textbf{Team Leader}, Data and Knowledge Management Lab, SJTU \\ACM RecSys Challenge 2016}
%}
%\begin{itemize}
%\setlength{\itemsep}{0pt}
%\setlength{\parskip}{0pt}
%\setlength{\parsep}{0pt}
%\item {\small Applied K-means algorithm to realize user and job clustering}
%\item {\small Built recommendation system model with given user features and predicted job postings that a user would click on for specified users}
%\end{itemize}
%------------------------------------------

{
\small
{\bf 32-bit Pipelined Processor Simulation} \hfill Sept. 2015 --- Dec. 2015\\
{\it \textbf{Team Leader}, UM-SJTU JI}
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Realized both single-cycle and pipelined MIPS-Architecture CPU in Verilog based on FPGA board}
\end{itemize}
\vspace{-.1 in}
{
\small
{\bf AFL Football Matches Prediction Modeling} \hfill Aug. 2015 --- Sept. 2015\\
{\it Data \& Knowledge Management Lab, Shanghai Jiao Tong University \\ CIKM Machine Learning Competition 2015, Final Rank (16/33)}
}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item {\small Selected effective features for Australian Rules Football games and applied Logistic Regression Model to obtain prediction results}
\end{itemize}
\vspace{-.1 in}
%--------------------------
\section{HONORS\&\\AWARDS}
{
\small
Shanghai Outstanding Graduates \hfill May. 2017\\
Capstone design Silver Award of JI Design Expo \hfill Dec. 2016\\
SJTU Outstanding Undergraduate Scholarship {(Top 10\% in SJTU)}\hfill2014\&2015\&2016\\
Dean's List {(term GPA$>$3.5)} \hfill2014\&2015\&2016\\
%Honorable Mention of Mathematical Contest In Modeling (MCM) \hfill2014\\
ACM International Collegiate Programming Contest Jing Hua Division, Silver Medal\hfill 2013\\
}
%--------------------------


%{\small \bf EXTRA CURRICULAR}
%\begin{itemize}
%\setlength{\itemsep}{0pt}
%\setlength{\parskip}{0pt}
%\setlength{\parsep}{0pt}
%\item {\small Elected {\it Machine Learning, Stanford University} in Coursera.org}
%\end{itemize}
%{\small \bf ACTIVITIES}
%\begin{itemize}
%\setlength{\itemsep}{0pt}
%\setlength{\parskip}{0pt}
%\setlength{\parsep}{0pt}
%\item {\small College Basketball team, UM-SJTU JI, Member}
%\item {\small Student Union Department of Publicity, UM-SJTU JI, Member}
%\end{itemize}

\end{resume}
\end{document}
